% Bairstow Bibliography

\bibitem{miller2014numerical} Miller, G. {\em Numerical Analysis for Engineers and Scientists.} 2014. Cambridge University Press. Pags. 175 - 178.

\bibitem{rosloniec2008fundamental} Rosloniec, S. {\em Fundamental Numerical Methods for Electrical Engineering.} 2008. Lecture Notes in Electrical Engineering - Springer Berlin Heidelberg. Pags. 30 - 35.

% Cholesky Bibliography

\bibitem{ipsen2009numerical} Ipsen, I.C.F. {\em Numerical Matrix Analysis: Linear Systems and Least Squares.} 2009. SIAM e-books - Society for Industrial and Applied Mathematics (SIAM, 3600 Market Street, Floor 6, Philadelphia, PA 19104). Pags. 63 - 65.

\bibitem{yang2005applied} Yang, W.Y. and Cao, W. and Chung, T.S. and Morris, J. {\em Applied Numerical Methods Using MATLAB.} 2005. Wiley. Pags. 111 - 112.

\bibitem{quarteroni2014scientific} Quarteroni, A. and Saleri, F. and Gervasio, P. {\em Scientific Computing with MATLAB and Octave.} 2014. Texts in Computational Science and Engineering - Springer Berlin Heidelberg. Pags. 135 - 151.

\bibitem{suli2003introduction} Suli, E. and Mayers, D.F. {\em An Introduction to Numerical Analysis.} 2003. Cambridge University Press. Pags. 87 - 93.

\bibitem{cheney2007numerical} Cheney, E. and Kincaid, D. {\em Numerical Mathematics and Computing.} 2007. International student edition - Cengage Learning. Pags. 305 - 306.

\bibitem{gander2014scientific} Gander, W. and Gander, M.J. and Kwok, F. {\em Scientific Computing - An Introduction using Maple and MATLAB.} 2014. Texts in Computational Science and Engineering - Springer International Publishing. Pags. 88 - 94.

\bibitem{scott2011numerical} Scott, L.R. {\em Numerical Analysis.} 2011. Princeton University Press. Pags. 51 - 60.

\bibitem{zalizniak2008essentials} Zalizniak, V. {\em Essentials of Scientific Computing: Numerical Methods for Science and Engineering.} 2008. Elsevier Science. Pags. 199.

\bibitem{heath2005scientific} Heath, M.T. {\em Scientific Computing: An Introductory Survey.} 2005. Scientific Computing: An Introductory Survey - McGraw-Hill. Pags. 63 - 65.

\bibitem{watkins2004fundamentals} Watkins, D.S. {\em Fundamentals of Matrix Computations.} 2004. Pure and Applied Mathematics: A Wiley Series of Texts, Monographs and Tracts - Wiley. Pags. 32 - 48.

\bibitem{ford2014numerical} Ford, W. {\em Numerical Linear Algebra with Applications: Using MATLAB.} 2014. Elsevier Science. Pags. 267 - 280.

